Relevance-based Quantization of Scattering Features for Unsupervised Mining of Environmental Audio

### 2018-02-17 paper/structureScene.tex
Edit ASSR section

Given a set of $d$-dimensional feature vectors $X_u = \{x_1^u, \ldots, x_L^u\}$, extracted from the scene $s_u$, where $u=\lbrace 1,2,\ldots,U\rbrace$, we would like to partition $X_u$ into a set $C_u = \{c^u_1, \ldots, c^u_M\}$ of $M$ clusters. The partitioning is done by minimizing squared error between the empirical mean, or centroid, of each cluster and the vectors belonging to it. This is known as $k$-means clustering \cite{lloyd} and has found widespread use for a variety of applications.
Each scene $s_u$ is then described by a set of clusters $C_u$. One should note that this quantization approach differs from unsupervised learning schemes such as the ones studied in \cite{bisot2016acoustic}, where the scene features are projected in a dictionary learned from the entire dataset. Here, with the aim of better balancing the influence of salient sound events and texture-like sounds on the final decision, the similarity between two scenes is computed based on the similarity of their centroids.

@@

To compute the similarity between two scenes, we consider several centroid-based similarity metrics:
\begin{itemize}
\item Relevance-based Quantization closest similarity (\emph{RbQ-c}): the similarity between two scenes $s_u$ and $s_v$ is equal to the largest similarity between their centroids, that is
\begin{equation}
	\max_{m,n} K_{mn}^{uv},
\end{equation}
\item Relevance-based Quantization average similarity  (\emph{RbQ-a}): the similarity between two scenes $s_u$ and $s_v$ is equal to the average of their centroid similarities, that is
\begin{equation}
	\frac{1}{M^2} \sum_{m,n} K_{mn}^{uv}
\end{equation}
and,
\item Relevance-based Quantization weighted similarity  (\emph{RbQ-w}): the similarity between two scenes is computed using a variant of the earth mover's distance applied to the set of centroids each weighted by the number of frames assigned to its cluster.
\end{itemize}

For \emph{RbQ-w}, each scene is represented by a signature
$$
p_u = \lbrace(\mu_1^u,w_1^u),(\mu_2^u,w_2^u),\ldots,(\mu_M^u,w_M^u)\rbrace,
$$
where each of the $M$ centroids $\mu_1^u, \ldots, \mu_M^u$ are paired with corresponding weights $w_1^u, \ldots, w_M^u$. The weight $w_m^u$ for the $m$th centroid $\mu_m^u$ is the number of frames belonging to a particular cluster. The similarity between scenes is then given by a cross-bin histogram distance known as the non-normalized earth mover's distance ($\widehat{\EMD}$) introduced by \cite{pele2008linear}. The $\widehat{\EMD}$ computes the distance between two histograms by finding the minimal cost for transforming one histogram into the other, where cost is measured by the number of transported histogram counts multiplied with the ``ground distance'' between the histogram bins. %In our case, the histogram counts are the clusters weights $w_m^u$ defined over the bins formed by the centroids $\mu_m^u$, so the ground distance is the centroid distance. \ml{From what we have below, the distance is not actually the distance between centroids, though. It's given by the kernel $K_{mn}^{uv}$.}

%\ml{Do we need the details that follow? Is it not enough to refer to \cite{pele2009fast}?}
%To compute the $\widehat{\EMD}$, we use the implementation proposed in \cite{pele2009fast}. Given two signatures $p_u$ and $p_v$, the $\widehat{\EMD}$ is computed by solving the following linear program:
% \begin{equation}
% \begin{split}
% \widehat{\EMD}(p_u,p_v) &=\left( \min\limits_{\lbrace f_{nm}\rbrace} \sum\limits_{n,m} f_{nm}D_{nm}^{uv} \right) \\
% &+ \left|\sum\limits_{n} w_n^u - \sum\limits_{m} w_m^v  \right| \max\limits_{n,m}\lbrace  D_{nm}^{uv}\rbrace.
% \end{split}
% \end{equation}
%
% \begin{equation*}
% \mathrm{s.t.} \quad f_{nm}\geq0 \quad \sum\limits_{m} f_{nm} \leq w_n^u \quad \sum\limits_{n} f_{nm} \leq w_m^v
% \end{equation*}
%
% \begin{equation*}
% \sum\limits_{n,m}f_{nm} = \min\left( \sum\limits_{n} w_n^u ,\sum\limits_{m} w_m^v \right)
% \end{equation*}
% %\ja{Can we provide some interpretation for the different terms and constraints here?}
% where $\lbrace f_{nm} \rbrace$ is the flow between the cluster weights $w_n^u$ and $w_m^v$, that is, the amount transported from the $n^{\textrm{th}}$ bin to ``supply the demand'' of the $m^\textrm{th}$ bin. We denote by $D^{uv}$ the ground distance, a matrix containing the pairwise distances between the centroids sets $\mu^u$ and $\mu^v$ which is computed from $K$:
% \begin{equation*}
% D_{mn}^{uv}=1-K_{mn}^{uv}.
% \end{equation*}
% \ml{Note that this is not actually a distance.}

% To get the final similarity measure between the scenes $s_u$ and $s_v$, an extended Gaussian kernel $K^s$ is computed: %\cite{chapelle1999support,jing2003support}
% \begin{equation}
% \label{eq:ks}
% K_{uv}^s = \exp\left( - \dfrac{\widehat{\EMD}(p_u,p_v)}{A} \right) \\
% \end{equation}
% with $A$ a scaling parameter, set to the mean value of the $\widehat{\EMD}$ between all the scenes. The resulting kernel $K^s$ is known as an $\EMD$ kernel, and it should be noted that there is no guarantee that this kernel is positive definite. \ml{Is this kernel used anywhere? For similarity, do we not just use the EMD distance directly?}

>>>>

Given a set of $d$-dimensional feature vectors $X_u = \{x_1^u, \ldots, x_L^u\}$, extracted from the scene $s_u$, where $u=\lbrace 1,2,\ldots,U\rbrace$, we would like to partition $X_u$ into a set $C_u = \{c^u_1, \ldots, c^u_M\}$ of $M$ clusters. This partition is obtained by minimizing the variance of each cluster and known as a $k$-means clustering \cite{lloyd}.
Each scene $s_u$ is then described by a set of clusters $C_u$. Note that this quantization approach differs from unsupervised learning schemes such as the ones studied in \cite{bisot2016acoustic}, where the scene features are projected in a dictionary learned from the entire dataset. Here, with the aim of better balancing the influence of salient sound events and texture-like sounds on the final decision, the similarity between two scenes is computed based on the similarity of their centroids.

@@

To compute the similarity between two scenes, we consider several centroid-based similarity metrics:
\begin{itemize}
\item Relevance-based Quantization closest similarity (\emph{RbQ-c}): the similarity between two scenes $s_u$ and $s_v$ is equal to the largest similarity between their centroids
\begin{equation}
	\max_{m,n} K_{mn}^{uv},
\end{equation}
\item Relevance-based Quantization average similarity  (\emph{RbQ-a}): the similarity between two scenes $s_u$ and $s_v$ is equal to the average of their centroid similarities
\begin{equation}
	\frac{1}{M^2} \sum_{m,n} K_{mn}^{uv}
\end{equation}
and,
\item Relevance-based Quantization weighted similarity  (\emph{RbQ-w}): the similarity between two scenes is computed using a variant of the earth mover's distance applied to the set of centroids each weighted by the number of frames assigned to its cluster.
\end{itemize}

For \emph{RbQ-w}, each scene is represented by a signature
$$
p_u = \lbrace(\mu_1^u,w_1^u),(\mu_2^u,w_2^u),\ldots,(\mu_M^u,w_M^u)\rbrace,
$$
where each of the $M$ centroids $\mu_1^u, \ldots, \mu_M^u$ are paired with corresponding weights $w_1^u, \ldots, w_M^u$. The weight $w_m^u$ for the $m$th centroid $\mu_m^u$ is the number of frames belonging to a particular cluster. The similarity between scenes is then given by a cross-bin histogram distance known as the non-normalized earth mover's distance $\widehat{\EMD}$ introduced by \cite{pele2008linear}. The $\widehat{\EMD}$ computes the distance between two histograms by finding the minimal cost for transforming one histogram into the other, where cost is measured by the number of transported histogram counts multiplied by the a dissimilarity measure between the histogram bins. Here, that measure is given by $1-K_{mn}^{uv}$.
